---
title: "p8105_hw5_am5088"
author: "Anika Mitchell am5088"
output: github_document
---

load my necessary libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
    fig.width = 6,
    fig.asp = .6,
    out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
    ggplot2.continuous.colour = "viridis",
    ggplot2.continuous.fil = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

I've gone ahead and loaded my necessary libraries and set up plotting for this problem (tidyverse), and will now start to develop a function to address the following question:

Suppose you put 𝑛people in a room, and want to know the probability that at least two people share a birthday. For simplicity, we’ll assume there are no leap years (i.e. there are only 365 days) and that birthdays are uniformly distributed over the year (which is actually not the case).

**Write a function that, for a fixed group size, randomly draws “birthdays” for each person; checks whether there are duplicate birthdays in the group; and returns TRUE or FALSE based on the result.**


```{r write birthday function}
summary(cars)
```

## Problem 1 Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
